Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-08-26 writing/CONUS_AOD.qmd
Update citation style.
Change AERONET acknowledgment to snippet with count.

bibliography: references.json
csl: https://www.zotero.org/styles/atmospheric-measurement-techniques

@@

We thank the AERONET federation principal investigators and their staff for establishing and maintaining the 328 sun photometer sites used in this investigation.

>>>>

bibliography: references.json
csl: https://raw.githubusercontent.com/citation-style-language/styles/795ad0c77258cb7e01f3413123b5b556b4cb6a98/dependent/journal-of-geophysical-research-atmospheres.csl

@@

We thank the AERONET federation principal investigators and their staff for establishing and maintaining the `r uniqueN(dt$site)` sun photometer sites used in this investigation.
